---
title: "Normal form for spatial data"
author: "Michael Sumner"
date: "9 May 2016"
output: html_document
---


## Separate those data frames

Long-form tables often contain repeated elements. Using some new approaches for non-standard evaluation and tidy data techniques makes is easy to "separate and normalize" these tables. Some examples. 

The in-built quakes data set in R has a small number observations at the same location. 

```{r}
sum(duplicated(quakes[, c("long", "lat")]))
library(dplyr)
library(nf)
nf(quakes, -long, -lat)
```

The function `nf` allows the user to specify which attributes (columns) to treat as `data`, normalizing that table to unique cases and recording an index from the original struture. 

Why is this useful? 

## Spatial data are hierarchical

Say we have a series of animal tracks, with longitude, latitude, date-time, id of the animal and other observations of the animal (rather than its track). 

```{r}
tr <- data_frame(id = c(rep(1, 10), rep(2, 15)), 
                 long = 1:25, 
                 lat = rnorm(25) + id * 3, 
                 trip = c(rep(1, 10), rep(2, 6), rep(3, 9)), 
                 date = Sys.time() + seq(25) + sample(5, 25, replace = TRUE))

library(ggplot2)
ggplot(tr) + aes(x = long, y = lat, group = trip, col = factor(id)) + geom_line() + aes(x = long, y = lat, label = format(date, "%M:%S")) + geom_text()

```

We know these data are grouped in a hierarchical way, not only is there a grouping based on `id` there's also a trip for a given id, and we can have any number of vertex attributes - for spatial locations like longitude, latitude, time, height, depth, temperature. 

The `nf` function allows us to specify which attributes are part of the geometry, and which of the topology, although in this case there's still a one-to-one. 


```{r}
nf(tr, -long, -lat, -date)
ggplot(tr) + aes(x = long, y = lat, group = trip, col = factor(trip)) + geom_line()
```
